---
output:
  md_document:
    variant: markdown_github
---
```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE)
```


```{r}

library(pacman)
pacman::p_load(fredr, tidyverse, lubridate, tsibble, dplyr, tseries, grid,gridExtra, sparsevar, tsDyn,vars)


```



```{r,echo = FALSE}

FRED_API_KEY <- fredr_set_key("d3c88549b884b18ff71b2541742bd179")

```

```{r,echo = FALSE}
FFR_eff_nsa <- fredr(
  series_id = "BOGZ1FL072052006Q",
  observation_start = as.Date("1980-01-01"),
  observation_end = as.Date("2021-07-01")
) |> dplyr::select(date, value) |> rename(FFR = value)

```

```{r,echo = FALSE}

CPI <- fredr(
  series_id = "CPALTT01USQ661S",
  observation_start = as.Date("1980-01-01"),
  observation_end = as.Date("2021-07-01")
) |> dplyr::select(date, value)|> rename(CPI = value)

```


```{r,echo = FALSE}


GDP <- fredr(
  series_id = "GDPC1",
  observation_start = as.Date("1980-01-01"),
  observation_end = as.Date("2021-07-01")
) |> dplyr::select(date, value)|> rename(GDP = value)

```


```{r,echo = FALSE}



M1 <- fredr(
  series_id = "M1SL",
  observation_start = as.Date("1980-01-01"),
  observation_end = as.Date("2021-07-01"),
  frequency = "q") |> dplyr::select(date, value)|> rename(M1 = value)




```


```{r,echo = FALSE}

## NB NB NB Notice the last date, make sure all variables have same nimber of observations

Oil_prices1 <- fredr(
  series_id = "POILBREUSDQ",
  observation_start = as.Date("1990-01-01"),
  observation_end = as.Date("2022-01-01")
) |> dplyr::select(date, value)

Oil_prices2 <- fredr(
  series_id = "OILPRICE",
  observation_start = as.Date("1980-01-01"),
  observation_end = as.Date("1989-11-01"),
  frequency = "q"
) |> dplyr::select(date, value)

Oil_prices <- bind_rows(Oil_prices2, Oil_prices1) |> rename(Oil=value)

```

```{r,echo = FALSE}



Exchange_1 <- fredr(
  series_id = "DTWEXAFEGS",
  observation_start = as.Date("2006-01-02"),
  observation_end = as.Date("2021-07-01"),
  frequency = "q") |> dplyr::select(date, value)


Exchange_2 <- fredr(
  series_id = "DTWEXM",
  observation_start = as.Date("1980-01-01"),
  observation_end = as.Date("2005-10-01"),
  frequency = "q") |> dplyr::select(date, value)

Exchange <- bind_rows(Exchange_1, Exchange_2) |> rename(Exchange = value)
    
    
    
```

```{r,echo = FALSE}

df <- bind_cols(FFR_eff_nsa, CPI |> dplyr::select(CPI), GDP|> dplyr::select(GDP), M1|> dplyr::select(M1), Exchange|> dplyr::select(Exchange), Oil_prices|> dplyr::select(Oil))

df_trimmed <- df |> filter(date <= lubridate::ymd(20031001))


df1 <- df |> mutate(lCPI = log(CPI), lGDP = log(GDP), lM1 = log(M1), lExchange = log(Exchange), lOil = log(Oil), realM1 = (lM1-lCPI), infl = lCPI - lag(lCPI)) |> fill( infl, .direction ="up")




interestrate_tr <- ts(df1$FFR, start=c(1980,1), end=c(2003, 4), freq=4)
price_tr <- ts(df1$lCPI, start=c(1980,1), end=c(2003, 4), freq=4)
realGDP_tr <- ts(df1$lGDP, start=c(1980,1), end=c(2003, 4), freq=4)
exchangerate_tr <- ts(df1$lExchange, start=c(1980,1), end=c(2003, 4), freq=4)
oilprice_tr <- ts(df1$lOil, start=c(1980,1), end=c(2003, 4), freq=4)
monetaryaggregate_tr <- ts(df1$lM1, start=c(1980,1), end=c(2003, 4), freq=4)
real_monetaryaggregate_tr <- ts(df1$realM1, start=c(1980,1), end=c(2003, 4), freq=4)   #transformation to real monetary aggregate
inflation_tr <- ts(df1$infl, start=c(1980,1), end=c(2003, 4), freq=4)

interestrate <- ts(df1$FFR, start=c(1980,1), end=c(2021, 3), freq=4)
price <- ts(df1$lCPI, start=c(1980,1), end=c(2021, 3), freq=4)
realGDP <- ts(df1$lGDP, start=c(1980,1), end=c(2021, 3), freq=4)
exchangerate <- ts(df1$lExchange, start=c(1980,1), end=c(2021, 3), freq=4)
oilprice <- ts(df1$lOil, start=c(1980,1), end=c(2021, 3), freq=4)
monetaryaggregate <- ts(df1$lM1, start=c(1980,1), end=c(2021, 3), freq=4)
real_monetaryaggregate <- ts(df1$realM1, start=c(1980,1), end=c(2021, 3), freq=4)   #transformation to real monetary aggregate
inflation <- ts(df1$infl, start=c(1980,1), end=c(2021, 3), freq=4)
    
D_interestrate_tr <- diff(interestrate_tr)
D_price_tr <- diff(price_tr)
D_realGDP_tr <- diff(realGDP_tr)
D_exchangerate_tr <- diff(exchangerate_tr)
D_oilprice_tr <- diff(oilprice_tr)
D_monetaryaggregate_tr <- diff(monetaryaggregate_tr)
D_real_monetaryaggregate_tr <- diff(real_monetaryaggregate_tr)
D_inflation_tr <- diff(inflation_tr)

```


# Johansen's Methodology for Modeling Cointegration

1. Select the specification of the deterministic component. Here the $\bm{\Phi}_t \bm{D}_t= \bm{\mu}_t = \bm{\mu}_0 + \bm{\mu}_1 t$ term contains all deterministic parts, i.e. constants and trends. 
2. Pre-test the variables to conclude that they are (or may be) $I(1)$.
3. Estimate the unrestricted VAR in levels and check the adequacy of the model specification.
4. Impose the number of cointegrating relationships $r$ and execute normalization as necessary.
5. Estimate the resulting (reduced-rank) cointegrated VECM, interpret the economic dynamics of the model, and test further hypothesized restrictions.

## 1. Select the specification of the deterministic component.

```{r}

df1_tidy <- df1 |> dplyr::select(date,FFR, lCPI, lGDP, lM1, lExchange, lOil, infl, realM1) |> pivot_longer(cols = c(FFR, lCPI, lGDP, lM1, lExchange, lOil, infl,realM1), names_to = "Variable", values_to = "Value") |> arrange(date)


Variable_labels <- c("FFR"="Interest Rate","infl"="Inflation","lCPI"= "CPI","lExchange"= "Exchange Rate","lGDP" ="Real GDP","lM1"= "Money Aggregate","lOil"= "Oil Price","realM1"= "Real Money Aggregate")

gggg <- df1_tidy |> ggplot() +
    geom_line(aes(x = date, y = Value), alpha = 0.8, 
    size = 0.5) + 
    theme_bw() + theme(legend.position = "none") + labs(x = "", 
    y = "", title = "TRI of Brics Countries", subtitle = "Total Return Index using net dividends reinvested", 
    caption = "Note:\nBloomberg data used") +
    facet_wrap(~Variable, scales = "free_y",labeller = labeller(category=Variable_labels)) 
    
gggg

```

## 2. Pre-test the variables to conclude that they are (or may be) $I(1)$

### 2.1.Augmented Dickey-Fuller (ADF) test for unit roots

```{r}

adf_interestrate_tr <- ur.df(interestrate_tr, type = "trend", selectlags = c("AIC")) #fail to reject null of no unit root
adf_price_tr <- ur.df(price_tr, type = "trend", selectlags = c("AIC")) #fail to reject null of no unit root
adf_realGDP_tr <- ur.df(realGDP_tr, type = "trend", selectlags = c("AIC")) # fail ...
adf_oilprice_tr <- ur.df(oilprice_tr, type = "trend", selectlags = c("AIC")) #
adf_exchangerate_tr <- ur.df(interestrate_tr, type = "trend", selectlags = c("AIC"))
adf_monetaryaggregate_tr  <- ur.df(monetaryaggregate_tr, type = "trend", selectlags = c("AIC"))


summary(adf_interestrate_tr)

```

### 2.2.Augmented Dickey-Fuller (ADF) test for order of integration

```{r}

adf_D_interestrate_tr <- ur.df(D_interestrate_tr, selectlags = c("AIC")) #I(1)
adf_D_price_tr <- ur.df(D_price_tr, selectlags = c("AIC")) #fail to reject null of no unit root only at the 1% sign level #I(2)
adf_D_realGDP_trr <- ur.df(D_realGDP_tr, selectlags = c("AIC")) #I(1)
adf_D_exchangerate_tr <- ur.df(D_exchangerate_tr, selectlags = c("AIC")) #I(1)
adf_D_oilprice_tr <- ur.df(D_oilprice_tr, selectlags = c("AIC")) #I(1)
adf_D_monetaryaggregate_tr <- ur.df(D_monetaryaggregate_tr, selectlags = c("AIC")) #fail to reject null of no unit root only at the 1% sign level

## Now lets deal with the problem of the monetary aggregate I(2) be transforming it to the real monetary aggregate (mt - pt) and to inflation (change in price)

adf_real_monetaryaggregate_tr <- ur.df(real_monetaryaggregate_tr, type = "trend", selectlags = c("AIC")) #fail to reject null of no unit root

adf_D_real_montaryaggregate_tr <- ur.df(D_real_monetaryaggregate_tr , selectlags = c("AIC")) #reject the null, Therefore is I(1)

adf_inflation_tr <- ur.df(inflation_tr,selectlags = c("AIC")) #fail to reject the null of no unit root

D_adf_inflation_tr <- ur.df(D_inflation_tr,selectlags = c("AIC")) #reject the null. Thus inflation is I(1)

```

## 3. Estimate the unrestricted VAR in levels and check the adequacy of the model specification.

The order of lags of the unrestricted VAR(p) is selected based on the AIC criteria reported in table \ref{}


```{r}
VAR1 <- cbind(real_monetaryaggregate_tr, interestrate_tr, realGDP_tr, inflation_tr, exchangerate_tr, oilprice_tr)
colnames(VAR1) <- cbind("RealMonetaryAggregate", "InterestRate", "RealGDP", "Inflation", "ExchangeRate", "OilPrice")
#In the same order as the A matrix


VAR2 <- cbind(realGDP_tr, oilprice_tr, interestrate_tr, inflation_tr,exchangerate_tr ,real_monetaryaggregate_tr)

#In a similar order to the cointegration analysis of the restricted system
```

### 3.1.Determine the order of lag

```{r}
infocrit <- VARselect(VAR2, lag.max = 4, type = "trend") ##Similar results as in the paper. Lag length of 2

```


### 3.2.Check the model specification adequacy of the estimated unrestricted VAR in levels

A critical point is to test that errors are white noise. The Johansen Method is a ML method, i.e. limiting distributions are derived assuming normal errors:
   1.Robust to some deviations: some non-normality, heteroscedasticity
   2.Requires: i.i.d. errors with finite variance
   3.Hence the following is unacceptable: autocorrelated residuals, time-varying parameters, structural breaks


```{r}
VAR_unrestricted <- VAR(VAR2, p = 2, type = "trend")

roots_stability <- roots(VAR_unrestricted) ##Shows eigenvalues corresponding to stability

```



```{r, warning=FALSE}

 varUR.serial <- serial.test(VAR_unrestricted, lags.pt = 17) ## Fail to reject null of multivariate serial correlation


 varUR.serial2 <- serial.test(VAR_unrestricted, type = "BG", lags.bg = 16)  ## Fail to reject null of multivariate serial correlation
 
 
 varUR.arch <- arch.test(VAR_unrestricted, lags.multi = 4,multivariate.only = F) ##Evidence of heteroskedasticity. Look individually
 
 varUR.norm <- normality.test(VAR_unrestricted, multivariate.only = F) ## Evidence of non-normal errors. Look individually

 
 plot(varUR.serial)

```




```{r}

reccusum_test <- stability(VAR_unrestricted,type = "Rec-CUSUM") #In time series analysis, the CUSUM statistics use the sequence of residual deviations from a model to indicate whether the autoregressive model is misspecified.

 plot(reccusum_test)

```


```{r}

fluctuation_test <- stability(VAR_unrestricted,type = "fluctuation") ## Test for unstable parameter fluctuations. Both these

 plot(fluctuation_test)

```


## 4.Impose the number of cointegrating relationships $r$ and execute normalization as necessary.

### 4.1. Determine the number of cointegrating relationships

```{r}
Johansen_trace <- ca.jo(VAR2, type="trace", ecdet = c("trend") ,K=3, spec="transitory")

# test stat < CV where r <=2 : reject null of no cointegrating relationships

Johansen_eig<- ca.jo(VAR2, type="eigen" ,K=3,spec="transitory")

# test stat > CV for r=0 and r <=1. Hence, indicative of 1 cointegrating relationships. As done in the paper

summary(Johansen_eig)

```

### 4.2. Esitmate the cointegrating relationships


```{r}
VECM_ur <- VECM(VAR2,lag=2,r=1, estim="ML",  LRinclude =c("trend") )
summary(VECM_ur)
#extract coefficients for Beta and Pi matrix:

coefB(VECM_ur) #remember includes a restricted trend
coefPI(VECM_ur) 

#The Beta-restricted VECM:

beta_VECM_ur <- coefB(VECM_ur) 
beta_VECM_restr <- head(beta_VECM_ur,6)
beta_VECM_restr[3,1] <- 0
beta_VECM_restr[6,1] <- 0

VECM_r <- VECM(VAR2,lag=2,r=1, estim="ML",beta = beta_VECM_restr)
round(coefB(VECM_r),5)

summary(VECM_r)


toLatex(summary(VECM_r), parenthese="Pvalue")
options("show.signif.stars"=TRUE)

#check long coint values
   all.equal(VECM(VAR2, lag=1, estim="ML", r=1,include=c("none"),LRinclude =c("both"))$model.specific$beta, 
             cajorls(ca.jo(VAR2, K=2, spec="transitory", ecdet = "trend"), r=1)  $beta, check.attributes=FALSE)




```


```{r}

 HH <-  matrix(byrow = TRUE, c(1, 0, 0, 0, 0, 0 ,0,1, 0, 0, 0, 0, 0,0,1,0, 0, 0, 0, 0 ,0,1,0, 0, 0, 0, 0 ,0,1,0, 0, 0, 0, 0,0,0,0,0,0,0,0,1), 7, 6)

HH1 <-matrix(byrow = TRUE, c(1,  0, 0, 0, 0,0 ,1,0, 0, 0, 0, 0,1,0,0, 0, 0, 0, 1,0,0, 0, 0, 0, 1,0, 0, 0, 0, 0), 6, 5)

 H1 <-  matrix(byrow = TRUE, c(1, 0, 0, 0, 0, 0,1, 0, 0, 0, 0,0,0,0,0,0,0,1,0, 0, 0, 0,0,1, 0, 0, 0, 0,0,0,0,0,0,0,1), 7, 5)
 
 H2 <- matrix(byrow = TRUE, c(1, 0, 0, 0,0,1, 0, 0,  0,0,1,0,0,0,0,1,0,0, 0,0,0, 0, 0,0), 6, 4)

 blr <-  blrtest(Johansen_eig, H=H2, r=1)
    summary(blr)
    
    
VECM_r1 <- VECM(VAR2,lag=2,r=1, estim="ML" ,beta = blr@V[,1])
summary(VECM_r1)

VECM_r1$model.specific$beta


```



```{r}

 vecm.r1 <- cajorls(Johansen_trace, r = 1)
summary(vecm.r1)

```

```{r}


LR <- matrix(NA, nrow = 6, ncol = 6)





SR <- matrix(NA, nrow = 6, ncol = 6)
SR[1, 3] <- 0
SR[1, 5:6] <- 0
SR[2, 1] <- 0
SR[3, 1:2] <- 0
SR[4, 1:3] <- 0
SR[5, 1:4] <- 0
SR[6, 1:5] <- 0


SVECM_r <- SVEC(ca.jo(VAR1, type="trace", ecdet = "trend" ,K=4, spec="longrun"),LR = LR ,SR= SR, r=1, lrtest = T, boot = T)
summary(SVECM_r)

print(SVECM_r$Restrictions)

```





## 5. Estimate the resulting (reduced-rank) cointegrated VECM, interpret the economic dynamics of the model, and test further hypothesized restrictions.


```{r}



```






```{r,}
#coeffs <- summary(VECModelNew)$coefMat

#ect_coeffs <- coeffs[grep("ECT", rownames(coeffs)),]

#now we have a matrix of all of the ECT and variables


#need covariance of ecm terms in matrix 
#cov(ect_coeffs)
```


```{r}

#blrtest(z =Johansen_eig_2 , H = , r = 2)


```






```{r}
 vecm.fevd <- fevd(SVECM_r) #forecast error variance decomposition
 vecm.norm <- normality.test(SVECM_r)
 vecm.arch <- arch.test(SVECM_r)
 vecm.serial <- serial.test(SVECM_r)
 
```






```{r}
M_IRF <- irf(SVECM_r, impulse = "OilPrice", response = "RealMonetaryAggregate",
             n.ahead = 16, boot=T, runs = 100)

IR_IRF <- irf(SVECM_r, impulse = "OilPrice", response = "InterestRate",
             n.ahead = 16, boot=T, runs = 100)
GDP_IRF <- irf(SVECM_r, impulse = "OilPrice", response = "RealGDP",
             n.ahead = 16, boot=T, runs = 100)
I_IRF <- irf(SVECM_r, impulse = "OilPrice", response = "Inflation",
             n.ahead = 16, boot=T, runs = 100)
ER_IRF <- irf(SVECM_r, impulse = "OilPrice", response = "ExchangeRate",
             n.ahead = 16, boot=T, runs = 100)

IRF <- irf(SVECM_r, impulse = "OilPrice",
             n.ahead = 16, boot=T, runs = 100, )

M <- plot(M_IRF)
I <- plot(IR_IRF)
G <- plot(GDP_IRF)
In <- plot (I_IRF)
E <- plot(ER_IRF)

plot(IRF)
#plotIRFGrid(irf, eb, indexes, type, bands)

#grid.arrange(M, I, G, In, E)


```



